\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{}.

@@

Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.

@@

\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{Section:results_dinlet}

>>>>

In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .

@@

Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

@@

\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{section:results_dinlet}
